---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ensemblr <a href="https://www.pattern.institute/ensemblr/"><img src="man/figures/logo.svg" align="right" height="139" alt="ensemblr website" /></a>

[![CRAN status](https://www.r-pkg.org/badges/version/ensemblr)](https://CRAN.R-project.org/package=ensemblr)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

The goal of `{ensemblr}` is to provide an R client to the [Ensembl REST API](https://rest.ensembl.org/).

Please note that this package is still in its infancy and hence only a small fraction of the resources exposed by the Ensembl REST API are retrievable via `{ensemblr}`. You can check the functionality covered so far in [Ensembl REST API Coverage](https://maialab.org/ensemblr/articles/api_coverage.html).

## Installation

You can install the current, **very** experimental version of `{ensemblr}` with:

``` r
# install.packages("remotes")
remotes::install_github("ramiromagno/ensemblr")
```

## Cheatsheet

TODO

## Example

Retrieve human linkage disequilibrium information for variants within a 1 kilobase window centred on variant `'rs123'`:

```{r}
library(ensemblr)
get_ld_variants_by_window("rs123", genomic_window_size = 1L)
```

## Contributors

Please note that the `{ensemblr}` project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

## Logo

The `{ensemblr}` logo, `ensemblr.png`, is a derivative work of an illustration of ["The small DNA double helix in PDB entry 309d"](https://cdn.rcsb.org/pdb101/motm/tiff/119-DesignedDNACrystal_309d.tif) by [David S. Goodsell](https://ccsb.scripps.edu/goodsell/) and the [RCSB PDB](https://www.rcsb.org/), used under [CC-BY-4.0](https://creativecommons.org/licenses/by/4.0/). `ensemblr.png` is licensed under CC-BY-4.0 by Ramiro Magno.

## Similar projects

- R package rensembl by [David Winter](http://david-winter.info/): https://github.com/dwinter/rensembl
- Python package ensembl-rest by [Andrés García](https://agargar.wordpress.com/): https://github.com/Ad115/EnsemblRest
- Python package ensembl by [Katsuya Noguchi](https://twitter.com/kn): https://github.com/kn/ensembl
